Investigating soundscapes perception through acoustic scenes simulation.

### 2017-12-13 lafaySimulatedScenePerception.tex
up until results

\item \emph{analysis of the perceived pleasantness}: the goal is to evaluate whether the perceived pleasantness is in accordance with the pleasantness label given by the creators of the  i- and ni-scenes durint the experiment 1.a. To do so, we consider the differences between the average $\mathcal{A}_{scene}$ and the average $\mathcal{A}_{subject}$ for each type of scenes (i or ni). The significance is evaluated by a two-sample Student test for $\mathcal{A}_{scene}$ and by a paired-sample Student test for $\mathcal{A}_{subject}$;

@@

\item \emph{influence of the structural features on the perceived pleasantness}: the goal is to evaluate if structural features impact the perceived pleasantness. We look at linear correlations between these features and $\mathcal{A}_{scene}$. The Pearson correlation coefficient is used for that purpose;

@@

\item \emph{analysis of the semantic features}: the goal is to evaluate if specific classes are more frequently used to simulate a given type of environment (i or ni). A V-test is considered \citep{lebart2000statistique} \ml{ref en Anglais ?}. With $c$ being the total number of classes used for both types of environment, $c_k$ the number of classes used for a given type of scene $k$ ($k=\lbrace i,ni\rbrace$), $c_j$ the number of time a class $j$ has been used, and $c_{jk}$ the number of time a class $j$ has been used for a given type of scene $k$, the V-test tests the null hypothesis that the ratio $\frac{c_{jk}}{c}$ is not significantly different from the ratio $\frac{c_{jk}}{c_k}$. For each class $j$, and each environment type $k$, an approximation of the statistic value $V_{jk}$ is computed as follows:

@@

If the null hypothesis is rejected, the class $j$ is said to be typical with respect to the type of scene $k$. The typical classes are called \textbf{sound markers}. Testing is done for each class, at every level of abstraction, and separately for texture and event classes;

@@

where $\bigoplus$ is the \emph{exclusive-or}. Two scenes having similar source compositions will be close in such space. The use of Hamming distance allows us to take into account equally the presence and absence of classes. For measuring the intrinsic ability of the space to split the i- and ni-scene, we use a ranking metric named the precision at rank $k$ ($P@k$). The $P@k$ computes the precision obtained after the $k$ closest items of a given seed item have been found. Formally, for each $s_i$ scene (considered as seed), we compute the ratio between the number of $s_j$ scenes taken among the $k$ nearest neighbors of $s_i$ and sharing the same label than $s_i$ versus $k$. the $P@k$ is then the average of this ratio for all the items considered as search seeds;

@@

The statistical tests of significance are done with a critical threshold of $\alpha=0.05$. For the V-test, considering that a great number of classes is tested, a Bonferroni correction is applied. For the $p$-value, if $p\geq0.05$, the value is reported. If $0.01\leq p<0.05$, we only report $p<0.05$, otherwise we report $p<0.01$.

>>>>

\item \emph{analysis of the perceived pleasantness}: the goal is to evaluate whether the perceived pleasantness is in accordance with the pleasantness label given by the creators of the  i- and ni-scenes durint the experiment 1.a. To do so, we consider if there exist significative differences for the i- and ni-scenes of the average $\mathcal{A}_{scene}$ and the average $\mathcal{A}_{subject}$. The significance is evaluated by a two-sample Student test for $\mathcal{A}_{scene}$ and by a paired-sample Student test for $\mathcal{A}_{subject}$;

% GL comprends pas en francais

@@

\item \emph{influence of the structural features on the perceived pleasantness}: the goal is to evaluate if the structural features impact the perceived pleasantness. To do so, we consider linear correlations between these features and $\mathcal{A}_{scene}$. The Pearson correlation coefficient is used for that purpose;

@@

\item \emph{analysis of the semantic features}: the goal is to evaluate if specific classes are more frequently used to simulate a given type of environment (i or ni). To do so, a V-test is considered \citep{lebart2000statistique} \ml{ref en Anglais ?}. With $c$ being the total number of classes used for both types of environment, $c_k$ the number of classes used for a given type of scene $k$ ($k=\lbrace i,ni\rbrace$), $c_j$ the number of time a class $j$ has been used, and $c_{jk}$ the number of time a class $j$ has been used for a given type of scene $k$, the V-test evaluates the null hypothesis that the ratio $\frac{c_{jk}}{c}$ is not significantly different from the ratio $\frac{c_{jk}}{c_k}$. For each class $j$, and each environment type $k$, an approximation of the statistic value $V_{jk}$ is computed as follows:

@@

If the null hypothesis is rejected, the class $j$ is said to be typical with respect to the type of scene $k$. The typical classes are called \textbf{sound markers}. Testing is done for each class, at each level of abstraction, and separately for texture and event classes;

@@

where $\bigoplus$ is the \emph{exclusive-or}. Two scenes having similar source compositions will be close in such space. The use of Hamming distance allows us to take into account equally the presence and absence of classes. For measuring the intrinsic ability of the space to discriminate between the i- and ni-scenes, we use a ranking metric named the precision at rank $k$ ($P@k$). The $P@k$ computes the precision obtained after the $k$ closest items with respect to a given seed item have been found. Formally, for each $s_i$ scene (considered as seed), we compute the ratio between the number of $s_j$ scenes taken among the $k$ nearest neighbors of $s_i$ and sharing the same label than $s_i$ versus $k$. the $P@k$ is then the average of this ratio for all the items considered as search seeds;

@@

The statistical tests of significance are done with a critical threshold of $\alpha=0.05$. For the V-test, considering that a large number of classes is tested, a Bonferroni correction is applied. For the $p$-value, if $p\geq0.05$, the value is reported. If $0.01\leq p<0.05$, we only report $p<0.05$, otherwise we report $p<0.01$.
